\documentclass[a4paper, 11pt]{article}

\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage[numbers,sort&compress]{natbib}

\theoremstyle{definition}
\newtheorem{exercise}{Exercise}

\begin{document}
%%% Header starts
\noindent{\large\textbf{IS-521 Activity}\hfill
                \textbf{PGP} \\
         {\phantom{} \hfill Due Date: March 13, 2017 (before class)} \\
%%% Header ends

\section{Activity Overview}

In this activity, we learn how to securely encrypt your files and
personal emails with PGP. We are going to use GnuPG, an open-source
implementation for PGP.

\section{PGP Key-Signing Party}

The goal of this exercise is twofold: (1) students get to know each
other; (2) students establish the web of trust using GPG.
\begin{enumerate}
  \item Create a PGP key of your own with GPG.
  \item Push your public key to our web page (by opening a pull
    request).
  \item Meet your colleagues and exchange your public keys.
  \item A student who gets the most signatures will get an extra point
    (+1).
  \item You can also ask course staffs to sign your key.
\end{enumerate}

\section{Ethical Conduct Agreement}

Git allows us to sign tags and commits with your PGP key. Read this
web page~\cite{gitgpg} and configure your PGP key with Git, and follow
the steps below.

\begin{enumerate}
  \item Fork the repository at
    \url{https://github.com/KAIST-IS521/Agreement}.
  \item Copy from the \texttt{Agreement.md} file to
    \texttt{your\_github\_id.md}.
  \item Modify the new file appropriately: correct the date and the
    name.
  \item Commit and push your modification.
  \item Tag your commit with ``Agreement''.
  \item Sign the tag, and push it.
  \item Open a pull request.
\end{enumerate}

\section{Sending an encrypted E-mail}

In this exercise, your goal is to send an email that is signed by your
private key and encrypted by professor's public key. The content of
your email should contain the following line:
\begin{verbatim}
Your Name, Your GitHub ID, Your Student ID
\end{verbatim}. Your email should be sent to
is521-staff@softsec.kaist.ac.kr.

\bibliography{references}
\bibliographystyle{plainnat}

\end{document}
